Stellar multiplicity

### 2018-05-10 article/ms.tex
ack

\shorttitle{Stellar multiplicity}
\shortauthors{Casey \& Hogg}

@@

\author[0000-0003-2866-9403]{David W. Hogg}
\affiliation{Center for Cosmology and Particle Physics, Department of Physics,
    New York University, 726 Broadway, New York, NY 10003, USA}
\affiliation{Center for Data Science, New York University, 60 Fifth Ave, 
    New York, NY 10011, USA}
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 
    Heidelberg}
\affiliation{Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}

@@

\acknowledgements
- Gaia/DPAC
- Gaia archive?
- Gaia DR2 hack week at Flatiron

>>>>

\shorttitle{Stellar multiplicity}
\shortauthors{Casey et al.?}

@@

%\author[0000-0003-2866-9403]{David W. Hogg??}
%\affiliation{Center for Cosmology and Particle Physics, Department of Physics,
%    New York University, 726 Broadway, New York, NY 10003, USA}
%\affiliation{Center for Data Science, New York University, 60 Fifth Ave, 
%    New York, NY 10011, USA}
%\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 
%    Heidelberg}
%\affiliation{Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}

@@

\acknowledgements
- If these peeps are not co-authors: Hogg, Spina, Schlaufman.
- Gaia/DPAC
- Gaia archive?
- Gaia DR2 hack week at Flatiron
- ARC DP

%This work has made use of CosmoHub.

%CosmoHub has been developed by the Port d'Informació Científica (PIC), maintained through a collaboration of the Institut de Física d'Altes Energies (IFAE) and the Centro de Investigaciones Energéticas, Medioambientales y Tecnológicas (CIEMAT), and was partially funded by the "Plan Estatal de Investigación Científica y Técnica y de Innovación" program of the Spanish government.
